\documentclass[letterpaper,11pt]{article}

%------------------------------------------------
% Packages
%------------------------------------------------

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%------------------------------------------------
% PAGE SPACING (tight)
%------------------------------------------------

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.65in}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=0.18in}

%------------------------------------------------
% SECTION STYLE
%------------------------------------------------

\titleformat{\section}
{\large\bfseries}
{}{0em}{}
[\titlerule]

\titlespacing*{\section}
{0pt}{6pt}{3pt}

%------------------------------------------------
% SEPARATOR
%------------------------------------------------

\newcommand{\sep}{\hspace{0.35em}\textbar\hspace{0.35em}}

%------------------------------------------------
% CUSTOM COMMANDS
%------------------------------------------------

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
#3 & #4 \\
\end{tabular*}
\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\end{tabular*}
\vspace{-3pt}
}

\newcommand{\resumeItem}[1]{\item \small{#1}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%------------------------------------------------
% DOCUMENT START
%------------------------------------------------

\begin{document}

%------------------------------------------------
% HEADER
%------------------------------------------------

\begin{center}

{\fontsize{28}{32}\selectfont\bfseries Anvi Wadhwa}

\vspace{3pt}

\small
\href{mailto:anvi.wadhwa2024@vitstudent.ac.in}{Email}
\sep
+91 93190 86177
\sep
\href{https://github.com/anvisgit}{GitHub}
\sep
\href{https://linkedin.com/in/anvi-wadhwa}{LinkedIn}
\sep
\href{https://medium.com/@anviwadhwa7}{Medium}

\end{center}

%------------------------------------------------
% EDUCATION
%------------------------------------------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Vellore Institute of Technology (VIT Chennai)}
{Chennai, India}
{B.Tech in Computer Science}
{Aug 2024 -- May 2028}

\resumeItemListStart
\resumeItem{CGPA: 8.1/10}
\resumeItem{R\&D Lead, Business Innovation Community}
\resumeItem{Member, Microsoft Innovation Community (AI/ML)}
\resumeItem{Member, Hackclub (AI/ML and Blockchain)}
\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------------------
% RESEARCH INTERESTS
%------------------------------------------------

\section{Research Interests}

Computer Science undergraduate interested in reinforcement learning, probabilistic modeling, and quantitative finance. Current work focuses on policy-gradient methods, uncertainty quantification, sequential decision-making, algorithmic trading systems, and multimodal speech emotion recognition.

%------------------------------------------------
% EXPERIENCE
%------------------------------------------------

\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Computer Vision Research Intern}
{IIT (BHU) Varanasi}
{AI-Powered Rehabilitation and Mobility System}
{May 2025 -- Present}

\resumeItemListStart
\resumeItem{Built real-time physiotherapy system using MediaPipe, OpenCV, and Python.}
\resumeItem{Developed joint-angle tracking pipelines for hip, knee, and ankle motion analysis.}
\resumeItem{Engineered CSV-based motion logging system for longitudinal rehabilitation data.}
\resumeItem{Optimized system for CPU-only deployment on standard consumer hardware.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------------------
% RESEARCH PROJECTS
%------------------------------------------------

\section{Research Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{PPO vs GRPO for Solving Wordle}
{\hfill \href{https://github.com/anvisgit/Comparative-Analysis-Of-PPO-And-GRPO-for-Solving-Wordle}{GitHub}}

\resumeItemListStart
\resumeItem{Designed and trained PPO and GRPO reinforcement learning agents in a custom Wordle environment.}
\resumeItem{Compared training stability, sample efficiency, convergence behavior, and reward-shaping sensitivity under identical experimental conditions.}
\resumeItemListEnd

\resumeProjectHeading
{Algorithmic Trading with Reinforcement Learning}
{\hfill \href{https://github.com/anvisgit/Algorithmic-Trading-with-Reinforcement-Learning}{GitHub}}

\resumeItemListStart
\resumeItem{Built PPO-based trading agent for Indian equities using custom Gym environment.}
\resumeItem{Incorporated realistic transaction costs and position sizing constraints.}
\resumeItem{Outperformed Nifty 50 benchmark using Sharpe, Calmar, and drawdown metrics.}
\resumeItemListEnd

\resumeProjectHeading
{Speech Emotion Recognition via Multi-Branch 1D-CNN Fusion}
{\hfill \href{https://github.com/anvisgit/Feature-Adaptation-and-Model-Optimization-for-Emotion-Recognition-in-Speech}{GitHub}}

\resumeItemListStart
\resumeItem{Developed multi-branch 1D-CNN combining MFCC, Mel spectrogram, and Chroma features.}
\resumeItem{Achieved 75.7\% accuracy and 75.5\% macro F1-score on RAVDESS dataset.}
\resumeItemListEnd

\resumeProjectHeading
{Systematic Intraday Trading using GARCH Forecasts}
{\hfill \href{https://github.com/anvisgit/Systematic-Intraday-Trading-Using-GARCH-Forecasts-and-High-Frequency-Indicators}{GitHub}}

\resumeItemListStart
\resumeItem{Developed a volatility-driven intraday trading strategy using rolling GARCH forecasts and high-frequency market indicators to generate entry and exit signals.}
\resumeItem{Implemented statistical volatility modeling to dynamically adapt position sizing and trade timing based on forecasted risk regimes.}
\resumeItem{Backtested the strategy across multiple equity instruments using historical intraday data to evaluate robustness and generalization.}
\resumeItem{Evaluated performance using risk-adjusted metrics including Sharpe ratio, win rate, drawdown, and volatility-adjusted returns.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%------------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------------

\section{Technical Skills}

\textbf{Languages:} Python, Java

\textbf{Machine Learning:} Deep Learning, Reinforcement Learning, Computer Vision, NLP

\textbf{Tools:} PyTorch, TensorFlow, scikit-learn, OpenCV, NumPy, Pandas, Git

%------------------------------------------------
% CERTIFICATIONS
%------------------------------------------------

\section{Certifications}

\textbf{Machine Learning Specialization} — Coursera (Andrew Ng)
\sep
\textbf{Quantitative Finance} — IIT Kharagpur

\end{document}
